Logeti, Stockhausen and Koenig:\\Esthetics of Electronic Music

### 2015-09-12 manuscript.tex
Some bibtex improvements and TODOs
Darmstadt-Cologne background in history review

@@

@@

Gesticulated phrases appears in Remifications only for short periods, they are not characterize the composition as a hole.
Nevertheless, we can note two ``overly exaggerated'' phrases, where the primer is a bit more distinct in that manner: 3:36 - 3:45, 6:28 - 6:40.
One could argue that these are just dramatic phrases within the composition, but I suspect that this amount of vibrato in Ligeti's composition most present some decent amount of cynicism.

>>>>

Darmstadt of post Wold War II became an important center for modern music.
The city is located in the state of Hessen in central Germany, in the American zone of occupation of these days.
The summer courses were financial supported by the US military government with two goals:
first, to propagate American values in effort to reeducate the German population in preparation for the establishment of democratic institutions;
and second, to provide a meeting place where musicians from the former fascist or fascist-occupied areas might further their musical reeducation through exposure to styles and techniques that had been prohibited during the fascist years (\cite{darmstadt_oxford}).
Since the first Darmstadt summer course, in 1948, the focus was on current musical concepts;
at the time it was, especially electronic and serail music\footnote{Internationales Musicinstitut Darmstadt: www.internationales-musikinstitut.de/en/summer-course/history/210-history.html}.

In addition to Darmstadt summer courses, the electronic music studios of Colone were another prominent center for the Darmstadt-Cologne avant guard scene.
The studios were founded in 1951, focused on the creation of pure electronic or ``electroacoustic'' music.
It is believed that the term ``electroacoustic'' was coined by Meyer-Eppler, one of the founders of the studios, to distinguish themeselves from musique-concr{\`e}te that characterize the French electronic studios (\cite{nwdr}).

@@

TODO Add Frigyesi comments from her paper in the relevant places.

TODO Some introduction: Ligeti citations are self explanatory...

@@

Gesticulated phrases appears in Remifications only for short periods, they are not characterize the composition as a hole.
Nevertheless, we can note two ``overly exaggerated'' phrases, where the primer is a bit more distinct in that manner: 3:36 - 3:45, 6:28 - 6:40.
One could argue that these are just dramatic phrases within the composition, but I suspect that this amount of vibrato in Ligeti's composition most present some decent amount of cynicism.
TODO cite frigyesi to support this statement.
